---
title: 'Coursera Data Science Specialisation: Regression Models Course Project'
author: "Danny Chan"
date: "April 2015"
output: html_document
---

# Executive Summary

# Context
Motor Trend, a magazine about the automobile industry are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

* “Is an automatic or manual transmission better for MPG”
* "Quantify the MPG difference between automatic and manual transmissions"

This report will explore these two questions by conducting:

1. Exploratory Data Analysis & Statistical Inference; and
2. Regression Analysis.

# Exploratory Data Analysis & Statistical Inference
After loading in the dataset `mtcars`, let us first note what variables the dataset contains, and what they measure by using R's handy `?mtcars` help function.

Variable name   | Data Type     | Definition
:-------------- | :-------------| :-------------
mpg             | numeric       | Miles/(US) gallon   
cyl             | numeric       | Number of cylinders
disp            | numeric       | Displacement (cu. in.)
hp              | numeric       | Gross horsepower
drat            | numeric       | Rear axle ratio
wt              | numeric       | Weight (lb / 1000)
qsec            | numeric       | 1/4 mile time
vs              | numeric       | V/S
am              | numeric       | Transmission (0 = automatic, 1 = manual)
gear            | numeric       | Number of forward gears
carb            | numeric       | Number of carburetors



```{r, echo = FALSE, warning = FALSE}
library(ggplot2)
dB <- mtcars
g <- ggplot(dB, aes(factor(am), mpg, fill = factor(am)))
g <- g + geom_boxplot()
g <- g + geom_jitter(position = position_jitter(width = .1, height = 0))
g <- g + scale_colour_discrete(name = "Type")
g <- g + scale_fill_discrete(name = "Type", breaks = c("0", "1"), labels = c("Automatic", "Manual"))
g <- g + scale_x_discrete(breaks = c("0", "1"), labels = c("Automatic", "Manual"))
g <- g + xlab("")
g
```

















# Regression Analysis


```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo = FALSE, message = FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
